The Concurrent Calculi Formalisation Benchmark

### 2023-10-03 paper/paper.tex
Split challenges.tex into multiple files.
Add Daniel as an author to the paper
Change Lorenzo's affiliation to Liverpool.

\author{
     Marco Carbone \inst{1}\orcidID{0000-0001-9479-2632}
\and David Castro-Perez \inst{2}\orcidID{0000-0002-6939-4189}
\and Francisco Ferreira \inst{3}\orcidID{0000-0001-8494-7696}
\and Lorenzo Gheri \inst{4}\orcidID{0000-0002-3191-7722}
\and Frederik Krogsdal Jacobsen \inst{5}\orcidID{0000-0003-3651-8314}
\and Alberto Momigliano \inst{6}\orcidID{0000-0003-0942-4777}
\and Luca Padovani \inst{7}\orcidID{0000-0001-9097-1297}
\and Alceste Scalas \inst{5}\orcidID{0000-0002-1153-6164}
\and Martin Vassor \inst{4}\orcidID{0000-0002-2057-0495}
\and Nobuko Yoshida \inst{4}\orcidID{0000-0002-3925-8557}
}

\institute{
     IT University of Copenhagen \email{maca@itu.dk}
\and University of Kent \email{D.Castro-Perez@kent.ac.uk}
\and Royal Holloway, University of London \email{Francisco.FerreiraRuiz@rhul.ac.uk}
\and University of Oxford \email{lorenzo.gheri@cs.ox.ac.uk}, \email{martin.vassor@cs.ox.ac.uk}, \email{nobuko.yoshida@cs.ox.ac.uk}
\and Technical University of Denmark \email{fkjac@dtu.dk}, \email{alcsc@dtu.dk}
\and Università degli Studi di Milano \email{momigliano@di.unimi.it}
\and Università di Camerino \email{luca.padovani@unicam.it}
}

@@

\appendix
\section{Challenges}
\input{../challenges.tex}

>>>>

\author{
     Marco Carbone \inst{1}\orcidID{0000-0001-9479-2632}
\and David Castro-Perez \inst{2}\orcidID{0000-0002-6939-4189}
\and Francisco Ferreira \inst{3}\orcidID{0000-0001-8494-7696}
\and Lorenzo Gheri \inst{4}\orcidID{0000-0002-3191-7722}
\and Frederik Krogsdal Jacobsen \inst{5}\orcidID{0000-0003-3651-8314}
\and Alberto Momigliano \inst{6}\orcidID{0000-0003-0942-4777}
\and Luca Padovani \inst{7}\orcidID{0000-0001-9097-1297}
\and Alceste Scalas \inst{5}\orcidID{0000-0002-1153-6164}
\and Martin Vassor \inst{8}\orcidID{0000-0002-2057-0495}
\and Nobuko Yoshida \inst{8}\orcidID{0000-0002-3925-8557}
\and Daniel Zackon \inst{9}\orcidID{0000-0000-0000-0000}
}

\institute{
     IT University of Copenhagen \email{maca@itu.dk}
\and University of Kent \email{D.Castro-Perez@kent.ac.uk}
\and Royal Holloway, University of London \email{Francisco.FerreiraRuiz@rhul.ac.uk}
\and University of Liverpool \email{Lorenzo.Gheri@liverpool.ac.uk}
\and Technical University of Denmark \email{fkjac@dtu.dk}, \email{alcsc@dtu.dk}
\and Università degli Studi di Milano \email{momigliano@di.unimi.it}
\and Università di Camerino \email{luca.padovani@unicam.it}
\and University of Oxford \email{martin.vassor@cs.ox.ac.uk}, \email{nobuko.yoshida@cs.ox.ac.uk}
\and McGill University \email{daniel.zackon@mail.mcgill.ca}
}

@@

\appendix
\section{Challenges}
\input{../challenges/challenges.tex}
